---
output:
  md_document:
    variant: markdown_github
    
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# worldbet: Convert WorldBet to IPA

This package is quick-and-dirty way to convert worldbet ASCII characters into
different representations.

Here is how the conversions look in RStudio.

```{r, eval = FALSE}
library("worldbet")

# that
convert_bet_to_ipa("D@t")
#> [1] "ðæt"

# uh-oh
convert_bet_to_ipa("^?o")
#> [1] "ʌʔo"

convert_bet_to_ipa("wA)&_r")
#> [1] "wɑɾɚ"
```

From the command prompt (on Windows), R falls back to escape sequences during
the conversions.

```{r}
library("worldbet")

# that
convert_bet_to_ipa("D@t")

# uh-oh
convert_bet_to_ipa("^?o")

# water
convert_bet_to_ipa("wA)&_r")
```

## WorldBet specification

The table below shows the implementation of the WorldBet used in the package.

```{r, echo = FALSE}
library("dplyr", warn.conflicts = FALSE)
as_literal <- function(xs) sprintf("`%s`", xs)
worldbet_key %>% 
  mutate(HTML_Entity = as_literal(Entity),
         WorldBet = as_literal(WorldBet)) %>% 
  select(WorldBet, IPA = Entity, `HTML Entity` = HTML_Entity) %>% 
  knitr::kable(.)
```

